### 2023-03-20 main.tex
Removed parents names from dedication

\null  % Necessary to have text or command before \vfill for proper spacing
\vfill
\begin{center}
    To my parents, Amy and David, who were always willing\\
    to indulge another ``experiment'' in their kitchen sink
\end{center}
\vfill
\clearpage

\begin{center}
    \bfseries\Large Acknowledgements
\end{center}
\bigskip
If it takes a village to raise a child, then it must take at least three to raise a scientist. Over the years, I've had countless friends, teachers, and mentors. These relationships have shaped the person I am today, so I'm grateful to all the people who took time out of their busy lives to help me in ways both small and large. However, I want to single out the following people who had an especially important impact on my time in graduate school.\\\\
Thank you to my advisor, Mike, for supporting me as a scientist and a person in equal measure.\\\\
Thank you to my committee, Susan, Liana, and Priya, for giving me the pep talk I needed every year.\\\\
Thank you to my lab, Holli, Stadler, Ciera, Ashley, Victoria, Augusto, and Xiao-Yong, for creating a space where it's okay to ask questions. A special thank you to my bay mates, Jenna and Colleen, for getting me through the hard days with sound advice and a healthy dose of humor.\\\\
Thank you to my undergraduate research mentors, Cathy and Jessica, for teaching me the most exciting science is at the intersection of different fields.\\\\
Thank you to my parents, for everything.\\\\
Thank you to my brothers, Andrew and Daniel, for giving me thick skin in the way only big brothers can.\\\\
Thank you to all the friends I've made in California and the Bay Area, for the much-needed life outside work.\\\\
Finally, thank you to my partner, Joseph, for going on this crazy ride with me. I couldn't have done this without you.
\clearpage

>>>>

\null  % Necessary to have text or command before \vfill for proper spacing
\vfill
\begin{center}
    To my parents, who were always willing to indulge\\
    another ``experiment'' in their kitchen sink
\end{center}
\vfill
\clearpage

\begin{center}
    \bfseries\Large Acknowledgements
\end{center}
\bigskip
If it takes a village to raise a child, then it must take at least three to raise a scientist. Over the years, I've had countless friends, teachers, and mentors. These relationships have shaped the person I am today, so I'm grateful to all the people who took time out of their busy lives to help me in ways both small and large. However, I want to single out the following people who had an especially important impact on my time in graduate school.\\\\
Thank you to my advisor, Mike, for supporting me as a scientist and a person in equal measure.\\\\
Thank you to my committee, Susan, Liana, and Priya, for giving me the pep talk I needed every year.\\\\
Thank you to my lab, Holli, Stadler, Ciera, Ashley, Victoria, Augusto, and Xiao-Yong, for creating a space where it's okay to ask questions. A special thank you to my bay mates, Jenna and Colleen, for getting me through the hard days with sound advice and a healthy dose of humor.\\\\
Thank you to my undergraduate research mentors, Cathy and Jessica, for teaching me the most exciting science is at the intersection of different fields.\\\\
Thank you to my parents, Amy and David, for everything.\\\\
Thank you to my brothers, Andrew and Daniel, for giving me thick skin in the way only big brothers can.\\\\
Thank you to all the friends I've made in California and the Bay Area, for the much-needed life outside work.\\\\
Finally, thank you to my partner, Joseph, for going on this crazy ride with me. I couldn't have done this without you.
\clearpage
